### 2021-07-11 src/paper/data/rapid_test_demand.tex
Typos in the estimated param table and get rapid test demand data section ready for review.

Until mid April 72\% of workers were expected to receive a weekly test offer
\citep{BMWI2021, IZA2021}. However, according to surveys conducted in mid April
\citep{Betsch2021}, less than two thirds of individuals with work contacts receive a test
offer. Starting on April 19th employers were required by law to provide two weekly tests
to their employees \citep{Bundesanzeiger2021}. We assume that compliance is incomplete
and only 80\% of employers actually offer tests.

@@

After Easter the share of students receiving twice weekly tests is set to 75\%. This is
based on tests becoming mandatory in Bavaria \citep{BayerischeStaatskanzlei2021} and
North Rhine-Westphalia \citep{SchulministeriumNRW2021b} after their Easter breaks and
on the 19th in Baden-Württemberg \citep{KMBaWue2021}.

@@

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior, we take this as
the upper bound of private rapid test demand which is reached in the beginning of May. To
cover that many people are likely to have sought and done their first rapid test before
the Easter holidays to meet friends or family, we let the share of individuals doing
rapid tests in that time increase more rapidly than before and after. By end of March
25\% of individuals would do a rapid test due to a private reason.

All shares of individuals who would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{Share of Individuals Doing a Rapid Test.}
    \floatfoot{\noindent \textit{Note:} Rapid test demand can be triggered by individuals
    planning to have education contacts, work contacts, developing symptoms without
    access to a PCR test, having a household member with a positive test or symptoms. In
    each case whether a rapid test is done depends on how long it has been since the
    individual's last rapid test and her individual compliance parameters. As an example,
    take a worker in May. In that time workers are encouraged to test themselves twice
    weekly but there is no general requirement to test themselves. If the worker has not
    done a test within the last four days in our model she will demand a test if her
    (time-constant) compliance parameter belongs to the upper 60\% in the population.}
    \label{fig:rapid_test_demand}
\end{figure}

>>>>

Until mid April 72\% of workers were expected to receive a weekly test offer
\citep{BMWI2021, IZA2021}. However, according to surveys conducted in mid April
\citep{Betsch2021}, less than two thirds of individuals with work contacts receive a test
offer. Starting on April 19th employers were required by law to provide two weekly tests
to their employees \citep{Bundesanzeiger2021}. We assume that compliance is incomplete
and only 80\% of employers actually offer tests. We interpolate between these points
linearly, arriving at the blue line in Figure~\ref{fig:rapid_test_demand}.

@@

After Easter the share of students receiving twice weekly tests is set to 75\%. This is
based on tests becoming mandatory in Bavaria \citep{BayerischeStaatskanzlei2021} and
North Rhine-Westphalia \citep{SchulministeriumNRW2021b} after their Easter breaks and on
the 19th in Baden-Württemberg \citep{KMBaWue2021}. Again, we interpolate linearly between
these points and arrive at the purple line for teachers and the red line for school
students in Figure~\ref{fig:rapid_test_demand}.

@@

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior, we take this as
the upper bound of private rapid test demand which we estimate in our model to be reached
in the beginning of May. To cover that many people are likely to have sought and done
their first rapid test before the Easter holidays we add another point that we estimate
for the rapid test demand around Easter. Similarly, we estimate one point in mid March
when tests started to become available in grocery stores and pharmacies which we estimate
in our model. The resulting share of private rapid test demand is shown as the green line
in Figure~\ref{fig:rapid_test_demand}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{Share of Individuals Doing a Rapid Test.}
    \label{fig:rapid_test_demand}
    \floatfoot{\noindent \textit{Note:} Rapid test demand can be triggered by individuals
    planning to have education contacts, work contacts, developing symptoms without
    access to a PCR test, having a household member with a positive test or symptoms. In
    each case whether a rapid test is done depends on how long it has been since the
    individual's last rapid test and her individual compliance parameter. As an example,
    take a worker in May. In that time workers are encouraged to test themselves twice
    weekly but there is no general requirement to test themselves. If the worker has not
    done a test within the last four days in our model she will demand a test if her
    (time-constant) compliance parameter belongs to the upper 60\% in the population.}
    \label{fig:rapid_test_demand}
\end{figure}
